
\chapter{Introduction\label{ch:intro}}

Palmprint has been increasingly recognized as unique and stable biometric characteristics for personal authentication. In the past decade, various methods based on two dimensional (2-D) palmprint have been studied in depth. The 2-D recognition techniques have proved to achieve high accuracy~\cite{Kong:2009hj}.

In recent years, three dimensional (3-D) palmprint recognition devices emerge and are quite promising because of the additional depth information gathered.

Although the devices has been out for more than two years, most previous matching algorithms treat 3-D information as a supplement to 2-D texture images and used joint matching techniques to increase accuracy~\cite{Li:2011ur, Li:2010en, Zhang:2009dp, Zhang:2008kc, Zhang:2010uu}. Authentication with only the 3-D information has not been thoroughly studied. The amount of useful information carried by the 3-D data is still under investigation.

There are two major challenges:

\begin{enumerate}
	\item 3-D devices, compared to 2-D ones, are lower in resolution.
	\item The depth values are susceptible to movements of human hands and are therefore less stable than 2-D texture information of palmprints.
\end{enumerate}

David et al. explore a 3-D palmprint recognition approach by exploiting the 3-D structural information of the palm surface~\cite{Zhang:2009dp, Zhang:2008kc}. The structured light imaging is used to acquire the 3-D palmprint data, from which several types of unique features, including mean curvature image, Gaussian curvature image, and surface type, are extracted. A fast feature matching and score-level fusion strategy is proposed for palmprint matching and classification. Wei et al. propose an efficient joint 2D and 3D palmprint matching scheme~\cite{Li:2010en}. The principal line features and palm shape features are extracted and used to accurately align the palmprint, and a couple of matching rules are defined to efficiently use the 2D and 3D features for recognition. The experiments show that the proposed scheme can greatly improve the performance of palmprint verification. Wei et al. also present an efficient scheme for 3-D palmprint recognition~\cite{Li:2011ur}. They extract both line and orientation features after calculating and enhancing the mean-curvature image of the 3-D palmprint data. The two types of features are then fused at either score level or feature level for the final 3-D palmprint recognition.

Existing work has been done to utilize the 3-D information for palmprint classification and sorting. The global features proposed for that purpose are fast in matching speed but low in accuracy compared to 2-D techniques.

%TODO
In this paper, we propose extracting three novel global features from a 3D palmprint image: Maximum Depth (MD) at the center of the palm, Horizontal Cross-section Area (HCA) at different levels of the palm; and Radial Line Length (RLL) measured from the centroid to the boundary of the 3D palmprint. These features are then used to describe and classify the shape of the 3D palmprint using continuous classification. This involves first reducing the dimensionality of the features by treating these features as a column vector and applying Orthogonal Linear Discriminant Analysis (OLDA) [17]. We then improve the efficiency of palmprint recognition by indexing the database using coarse-level matching and Ranking Support Vector Machine (RSVM) [18]

The rest of the paper is organized as follows. Section 2 describes how we define a region of interest for the 3D palmprint image and then extract our three proposed global features. Section 3 describes how global features can be used in classification in order to speed up identification. Section 4 gives the experimental results and Section 5 concludes the paper.


The major contribution of this paper is a set of features that can increase the recognition performance of palmprint verification.
